%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Consultant} % Job title
    {Quantitative Trading Book in Ernst \& Young U.S. LLP} % Organization
    {New York, USA} % Location
    {Oct 2023 - Present} % Date(s)
    {
      \begin{enumerate}
        \item Derivatives Pricing Algorithm Project
        \begin{itemize}
          \item Led the modular redesign of derivatives pricing algorithm by decomposing it into service class and analysis units.
          \item This architecture ensured high decoupling of coding, enabling independent updates to each component without affecting the overall system, significantly reducing redundancy and enhancing maintainability.
          \item Designed and implemented robust unit testing frameworks, improving system debug reliability by proactively identifying potential errors.
        \end{itemize}
        \item Equity Derivatives Pricing Algorithm Enhancement
        \begin{itemize}
          \item Improved the pricing algorithm of equity derivatives by shifting from a market-based risk model to an underlying location-based risk analysis, enabling a more accurate and interpretable pricing framework.
          \item Combine advanced machine learning techniques, such as LSTM, random forest models with traditional MCMC methods to price derivatives, enabling the pricing of complex toxic options with more than three underlying.
        \end{itemize}
        \item Counterparty Credit Risk Monitoring Using SFT VaR-Based Models
        \begin{itemize}
          \item Employed SFT VaR-based models to calculate and monitor Counterparty Credit Risk.
          \item Interpreted complex data and model results to deliver clear insights to stakeholders, including cross-disciplinary teams and non-technical audiences.
          \item Continuously updated model parameters in line with evolving market data, ensuring the models reflect current market conditions and deliver accurate risk assessments.
        \end{itemize}
        \item Optimization of American Options Pricing
        \begin{itemize}
          \item Applied the American Monte Carlo (AMC) method to price American options, replacing the computationally intensive Monte Carlo over Monte Carlo method. This optimization reduced the computational complexity from O(n²) to O(n), significantly improving pricing speed and saving considerable computational resources.
        \end{itemize}
      \end{enumerate}
    }

%---------------------------------------------------------
  \cventry
    {Securities Analyst Assistant (intern)} % Job title
    {Bank of China International Holdings Limited} % Organization
    {Shanghai, China} % Location
    {Jun 2021-Sep 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Focused on battery and new energy industry. Predicted the short- and long-term performance of stocks of related companies based on time series model with a spike-and-slab error.}
        \item {Adjusted the prediction under a multinomial model based on the performance of correlated companies and avoided making an over-optimistic forecast compared with previous model.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Analyst (intern)} % Job title
    {HUATAI SECURITIES CO., LTD.（HTSC）} % Organization
    {Jiangsu, China} % Location
    {Jul 2017-Sep 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Unsupervised screened visitors with a strong desire to buy products based on their records on company’s APP.}
        \item {Cleaned and reshaped the 17 million visitor records by summarizing operations from the same visitor.}
        \item {Extracted useful variables by PCA (principal component analysis) method.}
        \item {Divided visitors into five groups by K-means methods and assigned visitors labels by their group.}
        \item {Fitted a decision tree with labeled data which could tag new visitor within 20 seconds while the target is 1 min.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
